Forecasting Gamma-Ray Bursts using Gravitational Waves

### 2018-08-06 Paper/Manuscript.tex
Shibata's book aded

Our computation for $T_\text{AW}$ is based on the Newtonian evolution of a binary system composed of two point masses in a quasi-circular Keplerian orbit. 
The long-term dynamics is governed by the radiation reaction of 
the GW emission from the system due to the time variance of the quadrupole moment of the binary.
Though the Newtonian (leading-order) treatment gives the 
inspiral time with better than $ 95\%$ accuracy,
we nonetheless supplement it with post-Newtonian corrections up to 3.5 post-Newtonian order (3.5PN) \cite{Blanchet_LRR}.
However, even that fails to provide an accurate depiction of the binary
evolution in the strong-field regime, where speeds $\gtrsim 0.1c$. This is a very complex and complicated problem requiring fully
numerical treatment in terms of general relativistic, magnetohydrodynamic codes 
with neutrino transport running on large-scale computing clusters and taking up to millions of CPU hours 
(see Ref.~\cite{Faber:2012rw} for a review, and Refs.~\cite{Baiotti:2016qnr,Kyutoku:2017voj, Zappa:2017xba, Dietrich:2018upm, Dietrich:2018phi} for the latest developments and references therein).
Despite its simple formulation, our quadrupole radiation driven Newtonian
evolution is more than sufficient to provide reliable estimations of advance warning times.
We support this claim in Sec.~\ref{sec:idealizations} with an extensive list of computations showing how much each of our approximations affects the inspiral time.

>>>>

Our computation for $T_\text{AW}$ is based on the Newtonian evolution of a binary system composed of two point masses in a quasi-circular Keplerian orbit. 
The long-term dynamics is governed by the radiation reaction of 
the GW emission from the system due to the time variance of the quadrupole moment of the binary.
Though the Newtonian (leading-order) treatment gives the 
inspiral time with better than $ 95\%$ accuracy,
we nonetheless supplement it with post-Newtonian corrections up to 3.5 post-Newtonian order (3.5PN) \cite{Blanchet_LRR}.
However, even that fails to provide an accurate depiction of the binary
evolution in the strong-field regime, where speeds $\gtrsim 0.1c$. This is a very complex and complicated problem requiring fully
numerical treatment in terms of general relativistic, magnetohydrodynamic codes 
with neutrino transport running on large-scale computing clusters and taking up to millions of CPU hours 
(see Ref.~\cite{Shibata_book, Faber:2012rw} for a review, and Refs.~\cite{Baiotti:2016qnr,Kyutoku:2017voj, Zappa:2017xba, Dietrich:2018upm, Dietrich:2018phi} for the latest developments and references therein).
Despite its simple formulation, our quadrupole radiation driven Newtonian
evolution is more than sufficient to provide reliable estimations of advance warning times.
We support this claim in Sec.~\ref{sec:idealizations} with an extensive list of computations showing how much each of our approximations affects the inspiral time.
